### 2021-09-23 sections/selected-training.tex
Update selected-training.tex

\begin{cvhonors}
\cvconf
{Longitudinal Networks with RSiena Workshop at the Pontifica Universidad Cat\'olica}
{Santiago, Chile}
{2018}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
{Montevideo, Uruguay}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Pontificia Universidad Ca\'olica Summer School in Mixed Methods}
{Santiago, Chile}
{2014}
\end{cvhonors}

>>>>

\begin{cvhonors}
\cvconf
{Longitudinal Networks with RSiena Workshop at the P Universidad Cat\'olica}
{Santiago, Chile}
{2018}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{Universidad Cat\'olica de Uruguay Winter School in Methods and Data Analysis}
{MVD, Uruguay}
{2015}
\end{cvhonors}

@@

\begin{cvhonors}
\cvconf
{P Universidad Ca\'olica Summer School in Mixed Methods}
{Santiago, Chile}
{2014}
\end{cvhonors}
